Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-17 main.Rmd
Fixed latex warning from m\choose 2

2. There will be $m$ time series variable corresponding to each level $A_i$ of $C_1$. We compute the pairwise differences in distributions of these $m$ time series variables. Thus there will be  ${m \choose 2}$ pairwise distances corresponding to each $A_i$.

@@

4. For each $i \in \{1, 2, \dots, l\}$, the maximum pairwise distance could be chosen from  ${m \choose 2}$ distances using $D_{i} = max(d_{jk})/m(max(d_{jk}) - min(d_{jk}))$ $\forall j, k = {1, 2, \dots, m}$. Here, maximum is being adjusted against the range of the data to accommodate for comparison of maximum distances for different ranges.

>>>>

2. There will be $m$ time series variable corresponding to each level $A_i$ of $C_1$. We compute the pairwise differences in distributions of these $m$ time series variables. Thus there will be  $\binom{m}{2}$ pairwise distances corresponding to each $A_i$.

@@

4. For each $i \in \{1, 2, \dots, l\}$, the maximum pairwise distance could be chosen from  $\binom{m}{2}$ distances using $D_{i} = max(d_{jk})/m(max(d_{jk}) - min(d_{jk}))$ $\forall j, k = {1, 2, \dots, m}$. Here, maximum is being adjusted against the range of the data to accommodate for comparison of maximum distances for different ranges.
